PH651 Assignment Five

### 2016-10-11 em/latex/HW2.tex
Add all.

>>>>

\section{Problem Two}
We let the radius of the internal dielectric be \textbf{a} and the outer dielectric have radius \textbf{b}. We then list the
boundary conditions for inner and outer potentials $\phi_1$ and $\phi_2$ and outer potential $\phi_o$.\\

\textbf{Boundaries}
\begin{align*}
  \phi_1(a) &= \phi_2(a)\\
  \phi_2(b) &= \phi_o(b)\\
  \frac{\partial \phi_1(a)}{\partial r} &= \frac{\partial \phi_2(a)}{\partial r}\\
  \frac{\partial \phi_2(b)}{\partial r} &= \frac{\partial \phi_o(b)}{\partial r}\\
  \phi(r>>b) &= -E_or\cos\theta
\end{align*}

Our solutions will take the general form:

\begin{align*}
  \phi &= \sum_{\ell = 0}^\infty \left(A_\ell r^\ell + \frac{B_\ell}{r^{\ell+1}}\right)P_\ell(\cos\theta)
\end{align*}

For the inner potential $\phi_1$ we don't permit any B-terms, since the inverse r would blow up at zero. For the middle potential $\phi_2$ we can apply no constraints. For the outer potential $\phi_o$ we say that all A are zero, else the potential would blow up at infinity. Thus:

\begin{align*}
  \phi_1 &= \sum_{\ell = 0}^\infty A^1_\ell r^\ell P_\ell(\cos\theta)\\
  \phi_2 &= \sum_{\ell = 0}^\infty \left(A^2_\ell r^\ell + \frac{B^2_\ell}{r^{\ell+1}}\right)P_\ell(\cos\theta)\\
  \phi_o &= -E_0r\cos\theta + \sum_{\ell = 0}^\infty \frac{B^o_\ell}{r^{\ell+1}}P_\ell(\cos\theta)
\end{align*}

We then apply our first two boundary conditions, noting that only the individual $\ell$ terms need to equal, not the whole summation:

\begin{align*}
  A^1_\ell a^\ell &= A^2_\ell a^\ell + \frac{B^2_\ell}{a^{\ell+1}}\\
  A^2_\ell b^\ell +& \frac{B^2_\ell}{b^{\ell+1}} = \frac{B^o_\ell}{b^{\ell+1}}\\
  A^2_1 b^1 +& \frac{B^2_1}{b^2} = -E_ob^1
\end{align*}

We then apply our derivative boundary conditions:

\begin{align*}
  \epsilon_r^1\ell A^1_\ell a^{\ell-1} =& \epsilon_r^2\ell A^2_\ell a^{\ell-1} - \epsilon_r^2\frac{\left(\ell+1\right)B^2_\ell}{a^\ell}\\
  \epsilon_r^2\ell A^2_\ell b^{\ell-1} -& \epsilon_r^2\frac{\left(\ell+1\right)B^2_\ell}{b^\ell}
  = -\epsilon_0\frac{\left(\ell+1\right)B^o_\ell}{b^\ell}\\
  \epsilon_r^2A^2_1 -2\frac{B_1^2}{b} &= -E_0
\end{align*}

If we solve for $A_1$ we get:
